Air cargo load and route planning in pickup and delivery operations

### 2024-01-26 latex/eswa.tex
Experiments. One more table to go.

%		\State $limit \gets 0.92$  \label{shims:limit}

@@

@@

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 1.2$\/ and $tmax =  3600s$}  \label{tab:20}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}}&$method$          & $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{Shortest} &\multirow{2}{*}{$Gurobi$} & $f$ & 8.52    & 11.70   & 13.07   & 13.54 & 12.44     &  1.00\\
		&                                                               &               {time (s)}  & 17      & 17      & 16      & 17    & 26        &  1.0 \\
		\cmidrule(lr){2-9}
		&                                                               \multirow{2}{*}{$Shims$}    & $f$ & 8.54    & 11.63   & 12.97   & 13.43 & 12.36     &  0.99 \\
		&                                                               &         {time (s)}        & 1       & 1       & 2       & 2     & 2         &  11.6 \\

@@

		\multirow{4}{*}{All $K!$}&                                  \multirow{2}{*}{$Gurobi$} & $f$ & 8.52    & 12.25   & 13.32   & 14.61  & \textbf{x}        & 1.00 \\
		&                                                               &               {time (s)}  & 25      & 36      & 121     & 297    & \textbf{x}        &  1.0 \\
		\cmidrule(lr){2-9}	
		&                                                               \multirow{2}{*}{$Shims$}    & $f$ & 8.54    & 12.26   & 13.23   & 14.53  & 13.42    & 0.99  \\
		&                                                               &         {time (s)}        & 1       & 2       & 6       & 17     & 106      & 18.4   \\
		\bottomrule

@@

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 1.5$\/ and $tmax =  3600s$}  \label{tab:50}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}} & $method$          & $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{ Shortest } & \multirow{2}{*}{$Gurobi$} & $f$ & 11.80 & 16.74 & 18.04 & 18.86 & 16.92 & 1.00 \\
		&&               {time (s)}                                                                  & 38    & 30    & 27    & 29    & 81    & 1.00  \\
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{$Shims$}                                                                    & $f$ & 11.83 & 16.74 & 18.01 & 18.89 & 16.91 & 1.00  \\
		&&         {time (s)}                                                                        & 1     & 2     & 2     & 3     & 3     & 20.5  \\

@@

		\multirow{4}{*}{All $K!$} & \multirow{2}{*}{$Gurobi$}                                  & $f$ & 11.81 & 17.01 & 18.25 & 20.59 & 18.36   & 1.00 \\ 
		&&               {time (s)}                                                                  & 53    & 61    & 193   & 470   & 2241    & 1.0  \\
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{$Shims$}                                                                    & $f$ & 11.83 & 17.00 & 18.21 & 20.45 & 18.00   & 0.99  \\ 
		&&         {time (s)}                                                                        & 1     & 2     & 9     & 26    & 157     & 15.5 \\
		\bottomrule

@@

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 2.0$\/ and $tmax =  3600s$}  \label{tab:100}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}}& $method$          & $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{Shortest} & \multirow{2}{*}{$Gurobi$} & $f$ & 17.75 & 24.39 & 26.46 & 27.09 & 24.00 & 1.00 \\ 
		&&                                                                               {time (s)}  & 162   & 95    & 74    & 68    & 67    & 1.0  \\
		\cmidrule(lr){2-9}	
		&                                                                   \multirow{2}{*}{$Shims$} & $f$ & 17.78 & 24.40 & 26.36 & 27.01 & 23.94 & 0.99  \\
		&&                                                                                {time (s)} & 2     & 3     & 3     & 4     & 5     & 27.4  \\

@@

		\multirow{4}{*}{All $K!$} & \multirow{2}{*}{$Gurobi$} & $f$ & 17.75 & 25.24 & 26.46 & 29.11 &  \textbf{x}   & 1.00 \\ 
		&&                                                                                {time (s)} & 151   & 123   & 319   & 689   &  \textbf{x}   & 1.0  \\
		\cmidrule(lr){2-9}	
		&                                                                \multirow{2}{*}{$Shims$}    & $f$ & 17.78 & 25.25 & 26.38 & 28.98 & 26.08 & 1.00  \\
		&&                                                                                {time (s)} & 2     & 3     & 13    & 37    & 229   & 23.3  \\
		\bottomrule

@@

\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item The strategy of testing all $K!$\/ tours often provide a better-quality solution, even with less time on each node. This shows that the four sub-problems are interconnected in such a way that it is not enough to solve them separately.
	\item $Gurobi$\/ fails in some cases when $scenario=5$\/ and the strategy is to check all $K!$\/ tours. This occurs because the runtime limit per node is smaller and there tend to be more packed contents on the aircraft, reducing the space for allocating items and making the solution difficult.
	\item When $Gurobi$\/ finishes, it finds the best solution, but the one obtained by $Shims$\/ reaches $99\%$\/ of that value.
	\item $Shims$\/ always finds a solution, being 11 to 27 times faster.
	\item All runtimes are much lower than the limit because the solution on many nodes can be fast. Anyway, in all the tests performed, the maximum time spent by $Shims$\/ did not reach 4 minutes. On the other hand, when $scenario=5$\/ and $surplus=1.5$, $Gurobi$\/ spent almost 40 minutes.
\end{itemize}

>>>>

@@

{\color{blue}
	After the items were generated, some experiments with the \textit{iRace} tool were executed to determine the values for parameters $threshold_1$ and $threshold_2$ used in \textit{Shims}, whose results are presented in Table \ref{tab:irace}.

	\begin{table}[H]
		\centering
		\caption{\textit{iRace} testing results}  \label{tab:irace}
		\footnotesize
		\begin{tabular}{cccc}
			\toprule
			\textbf{surplus} & \boldm{$threshold_1$} & \boldm{$threshold_2$} & \textbf{time (min)}\\
			\midrule
			1.2& 0.8621 & 1.0539 & 47 \\
			1.5& 0.9199 & 1.1399 & 59 \\
			2.0& 0.9617 & 1.5706 & 63 \\						
			\bottomrule
		\end{tabular}
		\normalsize
	\end{table}

	For these tests, we considered the odd instances (1, 3, 5, 7) as the \textbf{training} set and the even instances (2, 4, 6) as the \textbf{testing} set for the \textit{iRace} runs. We supplied \textit{iRace} for $threshold_1$ determination, the range [0.8, 1.0], and for $threshold_2$, the range [1.0, 2.0]. The number of iterations in each experiment was limited to 3000 executions for \textit{iRace} to have plenty of data for its statistical tests. More detail about these configurations may be found on the \textit{iRace} user guide in {\tt cran.r-project.org/web/packages/irace/irace.pdf}.

@@

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 1.2$\/ and $tmax =  3600s$}  \label{tab:20}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}}&$method$&$scenario$&{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&\specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{Shortest} &\multirow{2}{*}{$Gurobi$}  & $f$ & 8.61    & 11.56   & 13.67   & 13.87 & 12.48       &  0.9985 \\ % best 6028
		&                              &               {time (s)}   & 26      & 22      & 28      & 28    & 25          &  1.0    \\ % longer 129
		\cmidrule(lr){2-9}
		&                           \multirow{2}{*}{$Shims$}  & $f$ & 8.61    & 11.56   & 13.46   & 13.93 & 12.51       &  0.9965 \\
		&                             &                {time (s)}   & 1       & 1       & 1       & 1     & 1           &  25.8   \\

@@

		\multirow{4}{*}{All $K!$}&  \multirow{2}{*}{$Gurobi$} & $f$ & 8.60    & 12.20   & 13.66   & 15.00  & {\bf x}    & 0.9998 \\ % best 4947
		&                              &               {time (s)}   & 30      & 35      & 123     & 314    & {\bf x}    & 1.0 \\
		\cmidrule(lr){2-9}	
		&                           \multirow{2}{*}{$Shims$}  & $f$ & 8.61    & 12.20   & 13.46   & 14.99  & 13.35      & 0.9958  \\
		&                              &               {time (s)}   & 1       & 1       & 4       & 10     & 51         & 7.49   \\
		\bottomrule

@@

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 1.5$\/ and $tmax =  3600s$}  \label{tab:50}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}} & $method$          & $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{ Shortest } & \multirow{2}{*}{$Gurobi$} & $f$ & 11.76 & 16.29 & 18.02 & 19.42 & 16.35 & 0.9994 \\ % best 8189
		&&               {time (s)}                                   & 51    & 39    & 40    & 36    & 38    & 1.0 \\ 
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{$Shims$}                               & $f$ & 11.78 & 16.29 & 17.96 & 19.43 & 16.37 & 0.9993  \\
		&&         {time (s)}                                         & 1     & 1     & 2     & 2     & 2     & 25.5  \\

@@

		\multirow{4}{*}{All $K!$} & \multirow{2}{*}{$Gurobi$}   & $f$ & 11.76 & 16.37 & 18.01 & 20.95 & 17.60 & 0.9999 \\  % best 8469
		&&               {time (s)}                                   & 64    & 58    & 195   & 472   & 2258  & 1.0  \\
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{$Shims$}                               & $f$ & 11.78 & 16.29 & 17.99 & 20.93 & 17.50 & 0.9976  \\ 
		&&         {time (s)}                                         & 1     & 2     & 5     & 15    & 100   & 23.8 \\
		\bottomrule

@@

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus = 2.0$\/ and $tmax =  3600s$}  \label{tab:100}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\specialcell{{\bf Tested}\\{\bf tours}}}& $method$& $scenario$ & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{Shortest} & \multirow{2}{*}{$Gurobi$} & $f$ & 17.89 & 24.96 & 26.15 & 27.52 & 23.85 & 0.9996 \\ % best 12042
		&&                                              {time (s)}  & 183   & 87    & 73    & 79    & 71    & 1.0  \\
		\cmidrule(lr){2-9}	
		&                            \multirow{2}{*}{$Shims$} & $f$ & 17.94 & 24.96 & 26.03 & 27.43 & 23.73 & 0.9972  \\
		&&                                              {time (s)}  & 1     & 2     & 2     & 3     & 4     & 41.1  \\

@@

		\multirow{4}{*}{All $K!$} & \multirow{2}{*}{$Gurobi$} & $f$ & 17.90 & 25.44 & 26.15 & 29.13 &{\bf x}& 0.9994 \\ % best 9867
		&&                                               {time (s)} & 178   & 143   & 378   & 862   &{\bf x}& 1.0  \\
		\cmidrule(lr){2-9}	
		&                         \multirow{2}{*}{$Shims$}    & $f$ & 17.94 & 25.45 & 26.14 & 28.84 & 26.22  & 0.9970  \\
		&&                                               {time (s)} & 1     & 3     & 10    & 31    & 196    & 34.7  \\
		\bottomrule

@@

\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item The strategy of testing all $K!$\/ tours often provide a better-quality solution, even with less time on each node. This shows that the four sub-problems are interconnected in such a way that it is not enough to solve them separately.
	\item $Gurobi$\/ fails in some cases when $scenario=5$\/ and the strategy is to check all $K!$\/ tours. This occurs because the runtime limit per node is smaller and there tend to be more packed contents on the aircraft, reducing the space for allocating items and making the solution difficult.
	\item When $Gurobi$\/ finishes, it finds the best solution, but the one obtained by $Shims$\/ reaches {\color{blue}$99.9\%$}\/ of that value.
	\item $Shims$\/ always finds a solution, being {\color{blue}8 to 41} times faster.
	\item All runtimes are much lower than the limit because the solution on many nodes can be fast. Anyway, in all the tests performed, the maximum time spent by $Shims$\/ did not reach 4 minutes. On the other hand, when $scenario=5$\/ and $surplus=1.5$, $Gurobi$\/ spent almost 40 minutes.
\end{itemize}
